---
title: "PSY 8960 Final Project"
author: "Anthony Greco"
date: "`r Sys.Date()`"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../out"
    )
  })
---

```{r Script Settings and Resources, include=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

```{r Data Import and Cleaning, include = FALSE}
skinny_tbl <- readRDS(file = "../out/fulldataset.rds") %>% 
  mutate(across(.cols = c(Gender, Department, EducationField, JobRole), .fns = ~ factor(.)),
         "Turnover Status" = as.logical(str_replace_all(Attrition, c("No" = "FALSE", "Yes" = "TRUE"))),
         "Monthly Pay" = MonthlyIncome,
         "Job Satisfaction" = JobSatisfaction, 
         "Education Field" = EducationField,
         "Job Role" = JobRole)  %>%
  select("Monthly Pay", "Turnover Status", "Job Satisfaction", Department, EducationField, Gender, JobRole)
```

# **Reproducible Image and Online Resources**
*The interactive web app described below can be accessed by [clicking this link.](https://agreco003.shinyapps.io/people_dashboard/)*

**Explanation of Approach:**
First, all variables that would be displayed in plots were converted to what would make sense in the plots themselves, so I wouldn't have to transform most of them in the shiny app itself. Then, all variables designated as potential filters were converted to factors, making them easier to filter, group, or otherwise use later in the shiny app. Data was then exported to an RDS output for simplicity. 

Regarding the coding approach for the app itself, I started with my UI. It was simple enough: I needed 5 inputs from the user, and needed to produce 2 outputs from those inputs. Therefore, I used a simple layout--1 side panel for filters with a main panel for displayed outputs. The plot, which remains the same size in the app at all times, was the first output in the main panel, followed underneath by the means and standard deviations desired. Then, I moved to the server side. 

Based on the same skinny dataset, I wanted create two separate tables that would be updated dynamically and used for the output plot and table respectively. I produced the underlying table for each output using reactive functions, functions designed to be updated repeatedly and quickly as people change their selections in the app. The plot function filtered results based on inputs, while the table function removes columns based on inactive selectors (set to "All" in a given selector). To display these outputs, I used the user-selected inputs directly as often as I could, in an effort to prevent the need for additional if statements. After some learning about unquoting--using the "!!" operator to unquote a single object in a function and a sym() wrapper function to convert my dynamic inputs into character strings--I reduced the need for duplicate code and if statements! 

Render objects were then used to generate plots, and their outputs were added to the app's UI. Univariate plots were generated with a single outcome, selected by the user, and the filters selected by the user. Visually, I tried to keep these plots simple and appealing. The table output, underneath the plot, generated means and standard deviations for whichever outcome, and collection of filtering variables, the user selected -- all with a single function based on data class. A single if-else statement, with only one if, was used for the plot output. This allowed for specific formatting to set bin size for the Monthly Pay histogram, which was otherwise an eyesore. Collectively, this creates a single shiny app with two outputs, based on users' selections!

```{r Publication, include=FALSE}
saveRDS(skinny_tbl, file = "../out/skinnydataset.rds")
saveRDS(skinny_tbl, file = "../shiny/people_dashboard/skinnydataset.rds") #saved to both locations, one to preserve in the out folder (just in case) and one to run the app itself.
```